Adaptative neigbouring methods applied to telephonic base stations

### 2024-08-15 article.tex
Image cropping + amelioration prez crit + ...

Basically, the interset of this method, compared to the Delaunay triangulation, is that it is adding a first level of filtration for bad neighbouring connexions.

@@

\begin{table}[!b]
    \centering
    \caption{Summary of criteria values}
    \label{table:crit_summary}
    \begin{tabular}{clcc}
        \toprule
        \textbf{$\gamma_i$} & \textbf{Description} & \textbf{max\_distance} & \textbf{min\_angle} \\
        \cmidrule(lr){1-4}
        $\left[0, 1\right]$ & city center & $\unit[2]{km}$ & $5^\circ$ \\
        $\left]1, 2\right]$ & urban area & $\unit[5]{km}$ & $10^\circ$ \\
        $\left]2, 4\right]$ & extra-urban area & $\unit[10]{km}$ & $15^\circ$ \\
        $\left]4, \infty\right[$ & courntryside & $\unit[15]{km}$ & $20^\circ$ \\
        \bottomrule
    \end{tabular}
\end{table}

\begin{figure}[!t]
    \centering
    \boxed{\includegraphics[width=2.5in]{images/illus_crit/points.png}}
    \caption{Example of a Delaunay triangulation}
    \label{table:crit_pts}
\end{figure}

\begin{figure}[!b]
    \centering
    \boxed{\includegraphics[width=2.5in]{images/illus_crit/distance_elim.png}}
    \caption{Example of a Delaunay triangulation}
    \label{table:crit_dis}
\end{figure}

\begin{figure}[!t]
    \centering
    \boxed{\includegraphics[width=2.5in]{images/illus_crit/angle_elim.png}}
    \caption{Example of a Delaunay triangulation}
    \label{table:crit_ang}
\end{figure}

\begin{figure}[!b]
    \centering
    \boxed{\includegraphics[width=2.5in]{images/illus_crit/quadrant_elim.png}}
    \caption{Example of a Delaunay triangulation}
    \label{table:crit_qua}
\end{figure}

\begin{figure}[!t]
    \centering
    \boxed{\includegraphics[width=2.5in]{images/illus_crit/neighs.png}}
    \caption{Example of a Delaunay triangulation}
    \label{table:crit_nei}
\end{figure}

\subsubsection{Distance criterion}
Each \acrshort{bs} has its proper coverage area, which is not infinite. As a matter of fact, we need to suppress longer edges.

\subsubsection{Angle criterion}
For each \acrshort{bs}, a potential neighbour can be \og hidden\fg{} by another one which nearer because there is a too narrow angle between those two \acrshort{bs}.
This criterion, will therefore suppress the longest edge between two \acrshort{bs} separated by a too small angle. This is illustrated in Figure \ref{table:crit_ang}.

@@

>>>>

Basically, the interset of this method, compared to the Delaunay triangulation, is that it is adding a first level of filtration to suppress some neighbouring connexions.

@@

\begin{table}[!b]
    \centering
    \caption{Summary of criteria values}
    \label{table:crit_summary}
    \begin{tabular}{clcc}
        \toprule
        \textbf{$\gamma_i$} & \textbf{Description} & \textbf{\emph{max\_distance}} & \textbf{\emph{min\_angle}} \\
        \cmidrule(lr){1-4}
        $\left[0, 1\right]$ & city center & $\unit[2]{km}$ & $5^\circ$ \\
        $\left]1, 2\right]$ & urban area & $\unit[5]{km}$ & $10^\circ$ \\
        $\left]2, 4\right]$ & extra-urban area & $\unit[10]{km}$ & $15^\circ$ \\
        $\left]4, \infty\right[$ & courntryside & $\unit[15]{km}$ & $20^\circ$ \\
        \bottomrule
    \end{tabular}
\end{table}

\begin{figure}[!t]
    \centering
    \boxed{\includegraphics[width=2.5in]{images/illus_crit/points.png}}
    \caption{Example of a Delaunay triangulation}
    \label{fig:crit_pts}
\end{figure}

\begin{figure}[!b]
    \centering
    \boxed{\includegraphics[width=2.5in]{images/illus_crit/distance_elim.png}}
    \caption{Example of a Delaunay triangulation}
    \label{fig:crit_dis}
\end{figure}

\begin{figure}[!t]
    \centering
    \boxed{\includegraphics[width=2.5in]{images/illus_crit/angle_elim.png}}
    \caption{Example of a Delaunay triangulation}
    \label{fig:crit_ang}
\end{figure}

\begin{figure}[!b]
    \centering
    \boxed{\includegraphics[width=2.5in]{images/illus_crit/quadrant_elim.png}}
    \caption{Example of a Delaunay triangulation}
    \label{fig:crit_qua}
\end{figure}

\begin{figure}[!t]
    \centering
    \boxed{\includegraphics[width=2.5in]{images/illus_crit/neighs.png}}
    \caption{Example of a Delaunay triangulation}
    \label{fig:crit_nei}
\end{figure}

\subsubsection{Distance criterion}
When looking at the results of Delaunay triangulation, we realise that some edges, mostly on the border of $P$ are too long. Indeed, a \acrshort{bs} does not have an infinite coverage area.

As a consequence, for each \acrshort{bs} the neighbouring connexions that are longer than a certain value, called \emph{max\_distance}, are suppressed (cf. Table~\ref{table:crit_summary}).

\subsubsection{Angle criterion}
For each \acrshort{bs}, a potential neighbour can be \og hidden\fg{} by another one which nearer because there is a too narrow angle between those two \acrshort{bs}.
This criterion, will therefore suppress the longest edge between two \acrshort{bs} separated by a too small angle. This is illustrated in Figure~\ref{fig:crit_ang}.

@@

\subsection{Combining criteria}
As a matter of optimisation, criteria are applied one after another. For example, the base graph is Delaunay triangulation and we apply distance then angle.
The principle is that angle criterion will be applied on the Delaunay graph filtered with the distance criterion.

As a consequence, results differ according to the order in which the criteria are applied.

The best is Delaunay with distance and then angle.
